\toolname: Property-Based Testing for MPC Security

### 2024-03-11 paper/main.tex
add funding acknowledgments

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{natbib}

@@

\newcommand{\mynote}[2]
    {{\color{red} \fbox{\bfseries\sffamily\scriptsize#1}
    {\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}~}
%\newcommand{\mynote}[2]{}
\newcommand{\todo}[1]{\mynote{TODO}{#1}}

@@

%\author{First1 Last1}
%%\authornote{with author1 note}        %% and a great more deleted...

@@

% In this work we present and evaluate a statistical test of the security of MPC protocols.
% First we show how MPC security relates to inference and equivalence of probabilistic distributions,
% and then we demonstrate that existing tests of distributional equivalence can, with minor modification, be used to refute MPC security.
% Our tool is adaptable to the wide range of cryptographic security properties that can be defined in terms of distributional equivalence,
% and our tool is applicable to any software system that
% A) can be run 10k-1M times without great inconvenience, and
% B) allows certain intermediate values (of which consumed randomness is the least convenient) to be captured for analysis.

@@

The goal of this work is a tool that can detect mistakes in diverse MPC protocols.
% Such a tools is only useful if there if new protocols and implementations are being written.
% Therefore, while it is critical to demonstrate that our tool can detect errors manually edited into known-secure protocols,
% we \textit{also} need to show that the tool can detect a lack of security in entirely novel and maximally diverse protocols.
We evaluate the generality of the approach by randomly generating hundreds of protocols and testing them with different test parameters.
We also use a batch of randomly generated protocols to asses the effects of the three test parameters
(\texttt{iters}, \texttt{trainN}, and \texttt{testN})
on the test's power and runtime.

@@

>>>>

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
%\usepackage{natbib}

@@

\newcommand{\mynote}[2]
    {{\color{red} \fbox{\bfseries\sffamily\scriptsize#1}
    {\small$\blacktriangleright$\textsf{\emph{#2}}$\blacktriangleleft$}}~}
\newcommand{\todo}[1]{\mynote{TODO}{#1}}

@@

\author{\IEEEauthorblockN{Mako Bates}
\IEEEauthorblockA{\textit{University of Vermont} \\
Burlington, Vermont, US \\
mako.bates@uvm.edu
}
\and
\IEEEauthorblockN{Joseph P. Near}
\IEEEauthorblockA{\textit{University of Vermont} \\
Burlington, Vermont, US \\
jnear@uvm.edu
}
}

@@

@@

The goal of this work is a tool that can detect mistakes in diverse MPC protocols.
We evaluate the generality of the approach by randomly generating hundreds of protocols and testing them with different test parameters.
We also use a batch of randomly generated protocols to asses the effects of the three test parameters
(\texttt{iters}, \texttt{trainN}, and \texttt{testN})
on the test's power and runtime.

@@

\section*{Acknowledgments}

This material is based upon work supported by the National Science Foundation under Grant No. 2238442 and by the Cold Regions Research and Engineering Laboratory (ERDC-CRREL)
under Contract No. W913E521C0003. Any opinions, findings and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation or the Cold Regions Research and Engineering Laboratory.
